Talks

### 2024-09-15 talks.qmd
update

  - Britain has a rich industrial and scientific heritage, with an established and diverse research culture anchored within a world-leading University sector. Successfully sustaining and building on the reputation of British research means addressing the challenges and criticisms of how research culture has developed in the 21st century. I will review some of these challenges - hypercompetition and excessive workload, employment precarity, perverse metrics, unfortunate publishing practices, lack of transparency, irreproducibility of findings and threats to international collaboration - and suggest ways forward.

  - Research funders share some common concerns: how do they know if they are allocating funding in the way that is most effective, fair and best balances risks versus possible rewards? Although a large variety of different funding systems exist, rigorous evidence on how funding can be designed to promote the best outcomes is not common. I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future

@@

>>>>

- 16 December: "History of partial randomisation in research". At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.

@@

  - Britain has a rich industrial and scientific heritage, with an established and diverse research culture anchored within a world-leading University sector. Successfully sustaining and building on the reputation of British research means addressing the challenges and criticisms of how research culture has developed in the 21st century. I will review some of these challenges - hypercompetition and excessive workload, employment precarity, perverse metrics, unfortunate publishing practices, lack of transparency, irreproducibility of findings and threats to international collaboration - and suggest ways forward.
  - Slides: [PPT](https://docs.google.com/presentation/d/1YbnKHHsHI--njavxH7Kp_bdAzCU3UHQTkSEUzjZgfKc/edit?usp=sharing), [PDF](docs/shanghai2024-09-09.pdf)

  - Research funders share some common concerns: how do they know if they are allocating funding in the way that is most effective, fair and best balances risks versus possible rewards? Although a large variety of different funding systems exist, rigorous evidence on how funding can be designed to promote the best outcomes is not common. I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
  - Slides: [PPT](<https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](pujiang2024-09-08.pdf), [transcript](shanghai_transcript2024-09-08.pdf)<>
